The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-08 paper/ms.tex
Fix line indentations throughout

Other methods for computing actions are used in the literature. For example,
the St\"ackel Fudge method \citep{2016MNRAS.457.2107S}, which uses a single
St\"ackel potential (with analytic actions) to approximate the Galactic
potential \citep{1985MNRAS.216..273D,2012MNRAS.426.1324B}, was used in many
recent works exploring actions in the Galactic disk
\citep[e.g.][]{2019MNRAS.484.3291T,2018MNRAS.481.4093S,2018arXiv180803278T}.
For disk-like orbits, existing implementations of the St\"ackel Fudge method
are of acceptable accuracy, but since we also consider halo-like orbits in
this work (where the St\"ackel Fudge method is inaccurate) we choose to use
orbit integration and torus mapping throughout \citep{2016MNRAS.457.2107S}.

>>>>

Other methods for computing actions are used in the literature. For example,
the St\"ackel Fudge method \citep{2016MNRAS.457.2107S}, which uses a single
St\"ackel potential (with analytic actions) to approximate the Galactic
potential \citep{1985MNRAS.216..273D, 2012MNRAS.426.1324B}, was used in many
recent works exploring actions in the Galactic disk
\citep[e.g.][]{2019MNRAS.484.3291T, 2018MNRAS.481.4093S, 2018arXiv180803278T}.
For disk-like orbits, existing implementations of the St\"ackel Fudge method
are of acceptable accuracy, but since we also consider halo-like orbits in
this work (where the St\"ackel Fudge method is inaccurate) we choose to use
orbit integration and torus mapping throughout \citep{2016MNRAS.457.2107S}.
